### 2023-05-05 paper/localpsf.tex
noise figures :)

	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m1_psf.png}

@@

	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m3_psf.png}

@@

	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m4_psf.png}

@@

	\begin{subfigure}{0.24\textwidth}
		\includegraphics[scale=0.1]{m6_psf.png}

@@

	%\begin{subfigure}{0.05\textwidth}
	%	\includegraphics[scale=0.1]{mColorBar.png}
	%\end{subfigure}
	\caption{The log basal sliding parameter after $1$ (left), $3$ (second from left), and $4$ (third from left) Newton iterations, and the final Newton iterate (right). The PSF (5) preconditioner is constructed between Newton iterations 3 and 4.}

>>>>

	\begin{subfigure}{0.18\textwidth}
		\includegraphics[scale=0.075]{mstar_0.25noise_cropped.png}

@@

	\begin{subfigure}{0.18\textwidth}
		\includegraphics[scale=0.075]{mstar_0.12noise_cropped.png}

@@

	\begin{subfigure}{0.18\textwidth}
		\includegraphics[scale=0.075]{mstar_0.05noise_cropped.png}

@@

	\begin{subfigure}{0.18\textwidth}
		\includegraphics[scale=0.075]{mstar_0.02noise_cropped.png}

@@

	\begin{subfigure}{0.18\textwidth}
	\includegraphics[scale=0.075]{mstar_0.01noise_cropped.png}
	\caption{The log basal sliding parameter computed from the PDE-constrained optimization problem with noise levels: $25\%$ (left), $11\%$ (second from left), $5.0\%$ (third from left), $2.2\%$ (fourth from left), and $1.0\%$ (right). The PSF (5) preconditioner is constructed between Newton iterations 3 and 4. \todo{remove reference to newon iterates figure as this figure has a new significance}}
